Switch equivalence and weak prime domains for fusions

### 2024-01-19 fusione.tex
cose

\begin{lemma}[Uniqueness of pushouts complements]\label{lem:pocomp} 
Let $\X$ be a $\mathcal{M}$-adhesive category. Given $m\colon X\mto Y$ in $\mathcal{M}$ and $n\colon Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $n$ and $W_1=\cod{h_1}$, $W_2=\cod{h_2}$. Then there exists a unique isomorphism $f\colon W_1\to W_2$ making the following diagram commutative.
\[\xymatrix{&X \ar@{>->}[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[ddl]_{h_2}& Y \ar[d]^{n} \\ &W_1 \ar@{.>}[dl]^{f} \ar@{>->}[r]_{k_1} & Z \\ W_2 \ar@{>->}@/_.3cm/[urr]_{k_2}}\]

\end{lemma}
\begin{proof} By hypothesis
	$k_1$ and $k_2$, being the pushout of $m$, are elements of $\mathcal{M}$ and therefore are monomorphisms. In particular, $k_2$ is a monomorphism and this  entails at once the uniqueness of $f$.  Moreover, notice that the squares
	\[\xymatrix{X \ar@{>->}[r]^{m} \ar[d]_{h_1}& Y \ar[d]^{n}& X \ar[d]_{h_2}\ar@{>->}[r]^{m} & Y \ar[d]^{n}\\ W_1 \ar@{>->}[r]_{k_1} & Z & W_2 \ar@{>->}[r]_{k_2}& Z}\]
	are $\mathcal{M}$-pushouts and thus $\mathcal{M}$-Van Kampen.

Now, take the $\mathcal{M}$-pullback square
	\[\xymatrix{P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar@{>->}[d]^{k_1}\\ W_2 \ar@{>->}[r]_{k_2} & Z}\]
	Since $k_1\circ h_1=k_2\circ h_2$, there exists a unique $g\colon X\to P$ fitting in
	\[\xymatrix{X \ar@/^.3cm/[drr]^{h_1} \ar@{.>}[dr]^{g} \ar@/_.3cm/[ddr]_{h_2}\\ &P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar@{>->}[d]^{k_1}\\ &W_2 \ar@{>->}[r]_{k_2} & Z}\]
	We can then build the cubes
	\[\xymatrix@C=13pt@R=13pt{&X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_1} \ar[dl]_{p_2} & &X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_2} \ar[dl]_{p_1}\\ X  \ar@{>->}[dd]_{m}\ar[rr]^(.65){h_2} & & W_2 \ar@{>->}[dd]_(.3){k_2}& &  X  \ar@{>->}[dd]_{m}\ar[rr]^(.65){h_1} & & W_1 \ar@{>->}[dd]_(.3){k_1}\\&X\ar[rr]|\hole^(.65){h_1} \ar@{>->}[dl]^{m} && W_1 \ar@{>->}[dl]^{k_1} & &X\ar[rr]|\hole^(.65){h_2} \ar@{>->}[dl]^{m} && W_2 \ar@{>->}[dl]^{k_2}\\Y \ar[rr]_{n} & & Z & &Y \ar[rr]_{n} & & Z}\]

	Now, in both cubes the front and left faces are pullbacks, thus, by \Cref{lem:pb1}, their back face is a pullback too. Since $m\leq m$, \Cref{lem:varie} now entails that $k_1\leq k_2$ and $k_2\leq k_1$. Thus there exists an isomorphism $f\colon W_1\to W_2$ such that $k_1=k_2\circ f$. To see that $h_2=f\circ h_1$, we can compute:
	\begin{align*}
		k_2\circ f \circ h_1 & = k_1\circ h_1\\&= n\circ m\\&= k_2\circ h_2
	\end{align*}
	The claim now follows since $k_2$ is a monomorphism. \qedhere 
\end{proof}

@@

@@

@@

\end{lemma}
\begin{proof}  As a preliminary step, we are going to use \Cref{def:filler,def:switch} to get some diagrams.  First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_0, i_1)$, then we have
	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&H'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]

>>>>

\begin{lemma}\label{lem:radj}
Let $f\colon X\to Y$ be an arrow in an $\mathcal{M}$-adhesive category $\X$ and suppose that the left square below is a pushout while the  right one is a pullback, with $ m\colon M\to X$ and $n\colon N\to Y$ in $\mathcal{M}$.
\[\xymatrix{M \ar@{>->}[d]_{m}\ar[r]^{h}& Q \ar@{>->}[d]^{k} & P \ar[r]^{p_1} \ar@{>->}[d]_{p_2}& N \ar@{>->}[d]^{n}\\X\ar[r]_{f}&Y &X \ar[r]_f&Y\\}\]
Then $n\leq k$ if and only if $p_2\leq m$.
\end{lemma}
\begin{proof}  
	We start pulling back $n$ along $k$ and then pulling back the resulting arrow along $h$, getting the following two pullbacks square:
\[\xymatrix{B \ar@{>->}[d]_{b}\ar@{>->}[r]^{s}& N \ar@{>->}[d]^{n} & A \ar[r]^{r} \ar@{>->}[d]_{a}& B \ar@{>->}[d]^{b}\\Q\ar@{>->}[r]_{k}&Y &M \ar[r]_h&Q\\}\]
Notice that 
\begin{align*}
	f\circ m\circ a&=k\circ h\circ a\\&=k\circ b\circ r\\&=n\circ s\circ r
\end{align*}
	Thus there exists a unique $t\colon A\to P$ as in the diagram
\[\xymatrix{A \ar@{>->}[d]_{a} \ar@{.>}[dr]^{t}\ar[r]^{r} &B \ar@{>->}@/^.2cm/[dr]^{s} \\ M \ar@{>->}@/_.2cm/[dr]_{m}&P\ar[r]^{p_1}  \ar@{>->}[d]_{p_2}& N \ar@{>->}[d]^{n}\\ &X \ar[r]_{f} & Y}\]
	We can then consider the cube below, in which the front, right and back faces are pullbacks.
		\[\xymatrix@C=15pt@R=15pt{&A\ar@{>->}[dd]|\hole_(.65){a}\ar[rr]^{r} \ar[dl]_{t} && B \ar@{>->}[dd]^{b} \ar[dl]_{s} \\ P  \ar@{>->}[dd]_{p_2}\ar[rr]^(.7){p_1} & & N \ar@{>->}[dd]_(.3){n}\\&M\ar[rr]|\hole^(.65){h} \ar@{>->}[dl]^{m} && Q \ar@{>->}[dl]^{k} \\X \ar[rr]_{f} & & Y}\]
	We can notice that the left square is a pullback too. To see this it is enough to apply \Cref{lem:pb1} to the diagram
	\[\xymatrix{A  \ar@/^.4cm/[rr]^{s\circ r}\ar@{>->}[d]_{a} \ar[r]_{t}& \ar[r]_{p_1} P \ar@{>->}[d]^{p_2}& N \ar[d]^{c}\\ M \ar@/_.4cm/[rr]_{k\circ h}\ar@{>->}[r]^{m}& X \ar[r]^{f}& Y}\]

	The thesis now follows immediately from \Cref{lem:varie}.
\end{proof}

\begin{corollary}[Uniqueness of pushouts complements]\label{lem:pocomp} 
Let $\X$ be a $\mathcal{M}$-adhesive category. Given $m\colon X\mto Y$ in $\mathcal{M}$ and $f\colon Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $f$ and $W_1=\cod{h_1}$, $W_2=\cod{h_2}$. Then there exists a unique isomorphism $\phi\colon W_1\to W_2$ making the following diagram commutative.
\[\xymatrix{&X \ar@{>->}[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[ddl]_{h_2}& Y \ar[d]^{f} \\ &W_1 \ar@{.>}[dl]^{\phi} \ar@{>->}[r]_{k_1} & Z \\ W_2 \ar@{>->}@/_.3cm/[urr]_{k_2}}\]

\end{corollary}
\begin{proof}
	Consider the two pushout squares
		\[\xymatrix{M \ar[r]^{h_1}\ar@{>->}[d]_{m}& W_1 \ar@{>->}[d]^{k_1} & M \ar@{>->}[d]_{m} \ar[r]^{h_1}& W_2 \ar@{>->}[d]^{k_2}\\Y\ar[r]_{f}&Z &Y \ar[r]_{f}&Z}\]
	Since $\mathcal{M}$ is in $\mathcal{M}$, \cref{prop:pbpoad} guarantees that they are both pullbacks.
	  Since $m\leq m$, by \Cref{lem:radj} we get that now entails that $k_1\leq k_2$ and $k_2\leq k_1$. Thus there exists an isomorphism $\phi\colon W_1\to W_2$ such that $k_1=k_2\circ \phi$. To see that $h_2=\phi\circ h_1$, we can compute:
	\begin{align*}
		k_2\circ \phi \circ h_1 & = k_1\circ h_1\\&= n\circ m\\&= k_2\circ h_2
	\end{align*}
	The claim now follows since $k_2$ is a monomorphism. \qedhere 
\end{proof}

@@

\begin{definition}[Sequential independence]  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category. Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.

	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{m'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]

	\[\xymatrix@C=15pt{L \ar[d]_{m}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
	We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists. If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
\end{definition}

 Let $(i_0, i_1)$ and $(i'_0, i'_1)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
	\begin{align*}f'\circ i_0&=h\\&=f'\circ i'_0
	\end{align*}
	On the other hand, 
	$f'\colon D'\to H$ is  the pushout of $l'\colon K'\to L'$ and so it is in $\mathcal{M}$, implying $i_0=i'_0$. If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g\colon D\to H$ is in $\mathcal{M}$ too, hence, from the equation
	\begin{align*}
		g\circ i_1&=h \\&= g\circ i'_1
	\end{align*}
	we can deduce that $i'_0=i'_1$, too. Summing up, we have just proved the following.

	\begin{proposition}\label{rem:weak}
	Let $(\X, \R)$ be a linear DPO-rewriting system, then two direct derivations $\dder{D}$ and $\dder{D}'$ are weakly sequential independet if and only if they are sequential independent. 
\end{proposition}

We want to be able to exchange to switch the application of two rules used by two consecutive weakly independent direct derivations. This leads us to the following definition.

\begin{definition}[Switch]
 Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category and suppose that $\der{D}=\{\dder{D}_i\}_{i=0}^1$  is a derivation of length $2$ made by the following two weakly sequentially independent derivations $\dder{D}_0$, $\der{D}_1$, with independence pair $(i_0, i_1)$:
 	\[\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2}\]

 	Take another derivation $\der{E}=\{\der{E}_i\}_{i=0}^1$ with source $G_0$ and target $G_2$ and in which $\der{E}_0$, $\der{E}_1$ are
\[\xymatrix{L_{\der{E},0} \ar[d]_{m_{\der{E},0}}& K_{\der{E},0} \ar[d]^{k_{\der{E},0}}\ar[l]_{l_{\der{E},0}} \ar[r]^{r_{\der{E},0}} & R_{\der{E},0} \ar[d]^{h_{\der{E},0}} & L_{\der{E},1} \ar[d]_{m_{\der{E},1}}& K_{\der{E},1} \ar[d]^{k_{\der{E},1}}\ar[l]_{l_{\der{E},1}} \ar[r]^{r_{\der{E},1}} & R_{\der{E},1} \ar[d]^{h_{\der{E},1}}\\G_{0} & \ar[l]^{f_{\der{E},0}} D_{\der{E},0} \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} & G_{\der{E},1} & \ar[l]^{f_{\der{E},1}} D_{\der{E},1} \ar[r]_{g_{\der{E},1}}& G_{2}}\]
 	We say that $\der{E}$ is a
 	 	 \emph{switch} of $\der{D}$ along $(i_1, i_2)$ if
 	\begin{enumerate}
 		\item $\der{E}_0$ applies the rule used by $\der{D}_1$ and $\der{E}_1$ the one used by $\der{D}_0$, so that
 		\[(l_{\der{E},0}, r_{\der{E},0})=(l_1,r_1)  \qquad (l_{\der{E},1}, r_{\der{E},1})=(l_0,r_0)\]
 		\item there exists $j_1 \colon L_0\to D_{\der{E},0}$ such that  $m_0=f_{\der{E},0} \circ j_1$;
 		\item $m_{\der{E},0}= f_0\circ i_1$ and $m_{\der{E},1}= g_{\der{E}, 0}\circ j_1$. %and $h_{\der{E},1}= g_{1}\circ i_0$.
 	\end{enumerate}
\end{definition}

\begin{remark}\label{rem:fact}
	Notice that, since $f_{\der{E}, 0}$ is in $\mathcal{M}$, there is at most one $j_1\colon L_0\to D_{\der{E},0}$ such that $m_0=f_{\der{E}, 0} \circ j_1$.
\end{remark}

\begin{lemma}\label{lem:cose} Let $(\der{D}, \alpha, \omega)$ be a decorated derivation with $\der{D}=\{\dder{D}_i\}_{i=0}^1$,  and suppose that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$  and $\der{D}_1$. If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a switch of $\der{D}$ along $(i_0, i_1)$, then the following hold true:
	\begin{enumerate}
			\item the pullback square below is an $\mathcal{M}$-pushout;
			\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\ D_0 \ar[r]_{g_1}& G_1}\]
			\item there exist $q_0\colon P\to D_{\der{E},0}$, $q_1\colon P\to D_{\der{E},1}$ making the squares 
			\[\xymatrix{}\]
			commutative, moreover, they are all pushouts;
			\[\xymatrix{}\]
 		\item there exists an arrow $j_0\colon R_1\to D_{\der{E},1}$ such that 
 		\[h_{\der{E},0}=f_{\der{E},1}\circ j_0 \qquad h_1=g_{\der{E},1} \circ j_0\]
	\end{enumerate}
\end{lemma}
\begin{proof}
	Before starting with the proof of our claims, it is worth noticing that the definition of switchin gives us the following diagram:
			\[\xymatrix@R=28pt{&&R_0 \ar@/_1.15cm/[ddrr]_(.8){i_0}|(.68)\hole \ar[dr]^{h_0}&& L_1\ar@/^1.15cm/[ddll]^(.8){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar[ur]^{r_0}&& G_1 && K_1 \ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.94cm/[ddrr]_(.8){j_1}|(.31)\hole \ar[dr]^(.35){m_0}|(.6)\hole && D_0 \ar[dl]^{f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]_{g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar[dl]^(.35){h_1}|(.6)\hole\\&G_0 &&&&G_2\\L_1 \ar@/^.94cm/[uurr]^(.8){i_1} \ar[ur]_(.35){m_{\der{E},0}}|(.61)\hole&&D_{\der{E},0} \ar[ul]_{f_{\der{E},0}}\ar[dr]^{g_{\der{E},0}} &&D_{\der{E},1}\ar[ur]^{g_{\der{E},1}} \ar[dl]|(.5)\hole^(.7){f_{\der{E},1}} && R_0  \ar@/_.94cm/[uull]_(.8){j_1} \ar[ul]^{h_{\der{E},1}}\\&K_1 \ar[ur]_{k_{\der{E},0}} \ar[dr]_{r_1} \ar[ul]^{l_1}&&G_{\der{E},1}&& K_0 \ar[ur]_{r_0} \ar[ul]^{k_{\der{E},1}} \ar[dl]^{l_0} \\&& R_1 \ar[ur]_{h_{\der{E},0}}&& L_0 \ar[ul]^{m_{\der{E},1}} \ar@/_1.15cm/[uull]_(.6){j_1} }\]

			Let us turn to our statements.
	\begin{enumerate}
		\item We start noticing that 
		\begin{align*}
			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=k_1\circ f_1
		\end{align*}
		Thus there exists the dotted $u\colon K_1\to P$ in the diagram
		\[\]
		The thesis now follows applyin \Cref{lem:popb} to

		\item 
		\item  We already have an arrow $j_1\colon L_0\to D_{\der{E},0}$ such that
		\[m_{\der{E},1}=g_{\der{E},0}\circ j_1\]
		Therefore the thesis follows at once from the previous point.

	\item

\todo{ $\dder{E}_0$ and $\dder{E}_1$ are weak sequentially independent;

if $\der{E}'=\{\dder{E}'_i\}_{i=0}^1$ is another switching of $\der{D}$ along $(i_0, i_1)$, then there exist arrows.... such that the following diagram commutes:
}
In particular [...]
\begin{definition}\todo{switch}
	contenuto...
\end{definition}
\begin{remark}
Canonico
\end{remark}
\begin{corollary}\todo{inversione}
\end{corollary}
\begin{proof}
	contenuto...
\end{proof}

\begin{lemma}
	\todo{permutazione}
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}

\begin{lemma}\label{lem:swfill}
\todo{equi}
\end{lemma}
\begin{remark}
	\todo{tobias}
\end{remark}
\begin{remark}
	contenuto...
\end{remark}
\begin{proof}
	contenuto...
\end{proof}

@@

We want to be able to exchange to switch the application of two rules used by two consecutive weakly independent direct derivations
\begin{definition}
	contenuto...
\end{definition}

\begin{proposition}
	\todo{equi}
\end{proposition}
\begin{remark}
	contenuto...
\end{remark}
\begin{proof}
	contenuto...
\end{proof}

@@

\end{lemma}
\begin{proof}  As a preliminary step, we are going to use \Cref{def:filler,def:switch} to get some diagrams.  First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_0, i_1)$, then we have
	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&H'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
